### 2022-01-17 src-latex/main-paper.tex
Updates from Overleaf
more details in setup and results
Finished section 3.2
Start OCR eval part
Add protocol figs

\documentclass[runningheads,svgnames]{llncs}
%
\usepackage[]{graphicx}
\usepackage{amsmath}
\usepackage{hyperref}
\usepackage{cleveref}
% \usepackage{tikz}
% \usepackage{nth}
% \usepackage{subcaption}
\usepackage{booktabs}
% \usepackage{array}
\usepackage{orcidlink}

@@

\begin{document}
%
\title{A Benchmark of Named Entity Recognition Approaches in Historical Documents\\
Application to 19$^{th}$ Century French Directories%
% FIXME "19$^{th}$-Century" with dash?
\thanks{This work was supported by the French National Research Agency:
Project SoDuCo, grant ANR-18-CE38-0013. ???FIXME need acknowledgments for directory sources???}}
%
\titlerunning{A Benchmark of NER Approaches in Historical Documents}
%
\author{LISTE PROVISOIRE PAR ORDRE ALPHA\\
%
Nathalie Abadie\inst{1}\orcidID{0000-0001-8741-2398} \and
Edwin Carlinet\inst{2,3}\orcidID{1111-2222-3333-4444} \and
Joseph Chazalon\inst{3}\orcidID{2222--3333-4444-5555} \and
Bertrand Duménieu\inst{3}\orcidID{2222--3333-4444-5555}}
%
\authorrunning{F. Author et al.}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{INST, CITY, COUNTRY \and
INST, CITY, COUNTRY\\
\email{example@example.com}\\
\url{https://www.example.com} \and
INST, CITY, COUNTRY\\
\email{example@example.com}}
%
\maketitle              % typeset the header of the contribution
%
\begin{abstract}
\input{parts/00-abstract.tex}
\keywords{Historical documents \and Natural Language Processing \and Named Entity Recognition \and OCR noise \and Annotation cost.}
\end{abstract}

@@

>>>>

\documentclass[runningheads,svgnames]{llncs}
%
\usepackage[]{graphicx}
\usepackage{amsmath}
\usepackage{hyperref}
\usepackage{cleveref}
% \usepackage{tikz}
% \usepackage{nth}
% \usepackage{subcaption}
\usepackage{booktabs}
% \usepackage{array}
\usepackage{orcidlink}
\usepackage{subcaption} % Addition
\usepackage{multirow} % Addition
\usepackage{tabularx} % Addition
\usepackage{booktabs} % Addition
\usepackage{scalerel}
\usepackage{cleveref}

@@

% Comment 
% FIXME : delete before submission :)
\newcommand{\bertrand}[1]{\textcolor{violet}{Bertrand:~#1}}
\newcommand{\nathalie}[1]{\textcolor{purple}{Nathalie:~#1}}
\newcommand{\edwin}[1]{\textcolor{pink}{Edwin:~#1}}

% Customize table rendering
\setlength{\tabcolsep}{5pt}
\renewcommand{\arraystretch}{1.4}

\begin{document}
%
\title{A Benchmark of Named Entity Recognition Approaches in Historical Documents\\
Application to 19$^{th}$ Century French Directories%
% FIXME "19$^{th}$-Century" with dash?
\thanks{This work was supported by the French National Research Agency:
Project SoDuCo, grant ANR-18-CE38-0013. ???FIXME need acknowledgments for directory sources???}}
%
\titlerunning{A Benchmark of NER Approaches in Historical Documents}
%
\author{LISTE PROVISOIRE PAR ORDRE ALPHA\\
%
Nathalie Abadie\inst{1}\orcidID{0000-0001-8741-2398} \and
Edwin Carlinet\inst{2,3}\orcidID{1111-2222-3333-4444} \and
Joseph Chazalon\inst{3}\orcidID{2222--3333-4444-5555} \and
Bertrand Duménieu\inst{3}\orcidID{2222--3333-4444-5555}}
%
\authorrunning{F. Author et al.}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{LASTIG, Univ. Gustave Eiffel, IGN-ENSG, F-94160 Saint-Mandé, France\\
\email{nathalie-f.abadie@ign.fr}\\
\url{https://www.umr-lastig.fr/nathalie-abadie/} \and
INST, CITY, COUNTRY\\
\email{example@example.com}\\
\url{https://www.example.com} \and
CRH-EHESS, Paris, France\\
\email{bertrand.dumenieu@ehess.fr}\\ \url{http://crh.ehess.fr/index.php?5206}}
%
\maketitle              % typeset the header of the contribution
%
\begin{abstract}
\input{parts/00-abstract.tex}
\keywords{Historical documents \and Natural Language Processing \and Named Entity Recognition \and OCR noise \and Annotation cost.}
\end{abstract}

@@

\section*{Acknowledment}
This work is supported by the French National Research Agency (ANR), as part of the SODUCO project, under Grant ANR-18-CE38-0013.

### 2022-01-17 src-latex/parts/50-xp-setup.tex
Updates from Overleaf

% Move to metrics ?
All metrics are evaluated on the test set, yet the biased model performances on the development sets are added in the article material as additional information.

\subsection{Experiment 2: NER in noisy OCRed texts}
This experiment aims to evaluate the impact of the OCR used on the quality of the NER results. To this end, we use directory entries whose text has been extracted, corrected and annotated manually (see Section 3). This reference text is aligned with the text produced on the same entries by Tesseract and PERO OCR. The named entities annotated in the reference text are then projected into the OCRed texts. To make sure that all training, development and test datasets contain the same annotations, only the entries for which the same number of annotations are found in the reference text and in the OCRised texts are kept.Finally, the reference text is divided into three datasets, using the same method as in Experiment 1. Two additional test files are generated with exactly the same entries as the test file produced from the reference text: one from the text produced by PERO OCR and one from that produced by Tesseract.

In this experiment, the two best models of Experiment 1 are kept. Both of them are fine-tuned on the training dataset produced from the reference text. One of them is also pretrained on 845000 entries automatically extracted by PERO OCR.

\begin{itemize}
\item At least 1 run per dataset, more if possible.
\item Only use the best model; should be CamemBERT+pretrained
\item Train on reference gold, evaluate on reference gold AND ocr-gold (2 datasets)
\item split train/dev/test the same way than experiment 1. Use the exact same splitting for datasets so the clean test set, pero test set and tesseract test sets contains the same entries.
\end{itemize}

@@

\subsection{Parameters for each method}

\subsection{OCR systems}
\begin{itemize}
    \item original OCR
    \item Tesseract 4
    \item Pero
    \item other?
\end{itemize}

@@

we use spacy  for the CNN implementation and Huggingface for BERT.

will we use FLAIR as well? $\rightarrow$ No

>>>>

% Move to metrics ?
All metrics are evaluated on the test set, yet the biased model performances on the development sets are added in the article material for information.

\subsection{Experiment 2: NER in noisy OCRed texts}
This experiment aims to evaluate the impact of the OCR used on the quality of the NER results. To this end, we use directory entries whose text has been extracted, corrected and annotated manually (see Section 3). This reference text is aligned with the text produced on the same entries by Tesseract and PERO OCR. The named entities annotated in the reference text are then projected into the OCRed texts. To make sure that all training, development and test datasets contain the same annotations, only the entries for which the same number of annotations are found in the reference text and in the OCRised texts are kept. Finally, the reference text is divided into three datasets, using the same method as in Experiment 1. Two additional test files are generated with exactly the same entries as the test file produced from the reference text: one from the text produced by PERO OCR and one from that produced by Tesseract.

%\begin{itemize}
%\item At least 1 run per dataset, more if possible.
%\item Only use the best model; should be CamemBERT+pretrained
%\item Train on reference gold, evaluate on reference gold AND ocr-gold (2 datasets)
%\item split train/dev/test the same way than experiment 1. Use the exact same splitting %for datasets so the clean test set, pero test set and tesseract test sets contains the %same entries.
%\end{itemize}

@@

%\subsection{Parameters for each method}

\subsection{OCR systems parameters}
\begin{itemize}
    \item original OCR
    \item Tesseract 4
    \item Pero
    \item other?
\end{itemize}

@@

EX1: Pour chaque modèle train sur les 8 datasets * 5 runs, avec mêmes paramètres pour l’entraînement: early stopping  (patience = 3)

Ex 2: On garde CamemBERT et CamemBERT pretrained fine-tuned sur le train clean (patience = 5), validé avec dev clean. Teste les deux modèles sur les trois datasets de test.

### 2022-01-17 src-latex/parts/60-results.tex
Updates from Overleaf

\begin{table}[h!]
\centering
\caption{Experimental results of the NER models performances when trained on varying numbers of examples}
\begin{tabular}{llrrrrrrrr}
       & Trainset Size &  49   &  99   &  199  &  398  &  796  &  1593 &  3186 &  6373 \\
       & \% & 0.8   & 1.6   & 3.1   & 6.2   & 12.5  & 25.0  & 50.0  & 100.0 \\
\midrule\bottomrule
\multirow{3}{*}{\rotatebox{90}{F1 score}} & Camembert &  89.5 &  90.5 &  92.7 &  93.3 &  94.1 &  94.9 &  94.6 &  95.1 \\
       & Camembert-pretrained &  92.4 &  92.9 &  93.7 &  93.8 &  93.8 &  94.0 &  94.6 &  94.4 \\
       & SpaCy NER &  87.0 &  89.0 &  90.3 &  91.9 &  92.1 &  92.8 &  93.2 &  93.5 \\
\cline{1-10}
\multirow{3}{*}{\rotatebox{90}{Precision}} & Camembert &  87.4 &  88.7 &  91.5 &  92.7 &  93.3 &  94.9 &  93.9 &  95.1 \\
       & Camembert-pretrained &  91.2 &  91.9 &  92.9 &  93.0 &  93.0 &  93.2 &  94.2 &  93.9 \\
       & SpaCy NER &  85.6 &  87.7 &  90.0 &  92.0 &  92.4 &  92.8 &  93.1 &  93.7 \\
\cline{1-10}
\multirow{3}{*}{\rotatebox{90}{Recall}} & Camembert &  91.6 &  92.5 &  93.9 &  93.9 &  94.9 &  94.9 &  95.4 &  95.1 \\
       & Camembert-pretrained &  93.7 &  94.0 &  94.4 &  94.7 &  94.6 &  94.8 &  95.0 &  94.9 \\
       & SpaCy NER &  88.6 &  90.4 &  90.7 &  91.7 &  91.9 &  92.8 &  93.3 &  93.4 \\
\end{tabular}
\label{tab:experiment-1-models-performances}
\end{table}

\begin{figure}[h!]
	   \center{\includegraphics[width=\textwidth]
	       {images/experiment-1-models-performances.pdf}}
	  \vspace{3in}
	  \caption{\label{fig:f1-vs-trainsize} Models F1 score on unseen data vs trainset size}
\end{figure}

@@

\begin{tabular}{lrrrrrr}
{} & \multicolumn{3}{c}{Camembert.pretrained} & \multicolumn{3}{c}{Camembert} \\
{} &                  ref & pero-ocr & tesseract &       ref & pero-ocr & tesseract \\
\midrule
Precision &                 96.5 &     93.3 &      90.3 &      96.1 &     92.4 &      89.7 \\
Recall    &                 96.5 &     92.6 &      91.3 &      96.6 &     92.5 &      91.2 \\
F1 score        &                 96.5 &     92.9 &      90.8 &      96.4 &     92.5 &      90.5 \\
\bottomrule
\end{tabular}

\begin{table}[h!]
\caption{Camembert vs noise}
\centering
\begin{tabular}{ll|cc|c}
 & & \multicolumn{2}{c|}{Training data} & \\
 & & noisy & clean &   \\ 
\cline{1-4}
\multirow{3}{*}{Test data}& noisy gold (Tesseract) & f1 & f1 & \\
                            & noisy gold (Pero-OCR) & f1 & f1 & \\ 
                            & reference gold & f1 & f1 & \\ 
                            & reference gold & f1 & f1 & \\
\cline{1-4}
\end{tabular}
\end{table}

>>>>

\begin{table}[h!]
\centering
\caption{NER performances at entry-level for SpaCy NER, CamemBERT and CamemBERT-pretrained when fine-tuned with an increasing number of examples.}
\begin{tabular}{llrrrrrrrr}
       & Number of training examples &  49   &  99   &  199  &  398  &  796  &  1593 &  3186 &  6373 \\
       & \% & 0.8   & 1.6   & 3.1   & 6.2   & 12.5  & 25.0  & 50.0  & 100.0 \\
\midrule\bottomrule
\multirow{3}{*}{\rotatebox{90}{F1 score}} & Camembert &  89.5 &  90.5 &  92.7 &  93.3 &  \textbf{94.1} &  \textbf{94.9} &  \textbf{94.6} &  \textbf{95.1} \\
       & Camembert-pretrained &  \textbf{92.4} &  \textbf{92.9} & \textbf{93.7} &  \textbf{93.8} &  93.8 &  94.0 &  \textbf{94.6} &  94.4 \\
       & SpaCy NER &  87.0 &  89.0 &  90.3 &  91.9 &  92.1 &  92.8 &  93.2 &  93.5 \\
\cline{1-10}
\multirow{3}{*}{\rotatebox{90}{Precision}} & Camembert &  87.4 &  88.7 &  91.5 &  92.7 &  93.3 &  94.9 &  93.9 &  95.1 \\
       & Camembert-pretrained &  91.2 &  91.9 &  92.9 &  93.0 &  93.0 &  93.2 &  94.2 &  93.9 \\
       & SpaCy NER &  85.6 &  87.7 &  90.0 &  92.0 &  92.4 &  92.8 &  93.1 &  93.7 \\
\cline{1-10}
\multirow{3}{*}{\rotatebox{90}{Recall}} & Camembert &  91.6 &  92.5 &  93.9 &  93.9 &  94.9 &  94.9 &  95.4 &  95.1 \\
       & Camembert-pretrained &  93.7 &  94.0 &  94.4 &  94.7 &  94.6 &  94.8 &  95.0 &  94.9 \\
       & SpaCy NER &  88.6 &  90.4 &  90.7 &  91.7 &  91.9 &  92.8 &  93.3 &  93.4 \\
\end{tabular}
\label{tab:experiment-1-models-performances}
\end{table}

\begin{figure}[h!]
	   \center{\includegraphics[width=\textwidth]
	       {images/experiment-1-models-performances.pdf}}
	  \caption{\label{fig:f1-vs-trainsize} Precision, recall and f1 score from table~\ref{tab:experiment-1-models-performances}}.
\end{figure}

@@

\begin{table}
\caption{CamemBERT and CamemBERT-pretrained NER performances at entry-level on manually corrected and noisy OCRerd entries when fine-tuned on manually corrected entries.}
\begin{tabular}{lrrrrrr}
{} & \multicolumn{3}{c}{Camembert.pretrained} & \multicolumn{3}{c}{Camembert} \\
{} &                  ref & pero-ocr & tesseract &       ref & pero-ocr & tesseract \\
\midrule
Precision &                 96.5 &     93.3 &      90.3 &      96.1 &     92.4 &      89.7 \\
Recall    &                 96.5 &     92.6 &      91.3 &      96.6 &     92.5 &      91.2 \\
F1 score        &                 96.5 &     92.9 &      90.8 &      96.4 &     92.5 &      90.5 \\
\bottomrule
\end{tabular}
\end{table}
